---
title: "Field Baker's day at campus"
author: "Nadezda Carr"
date: "4/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TSP)
```

Young Field Baker is planning his trip to CSUB campus.  He must make 5 stops and one visit to a restroom.  He starts and ends the day at the bus stop on campus

The stops he must make and the North, East coordinates of each are givnen in the following table: (units are Cubits)

   Location     |  coordinates (N, W)
   -------------|--------------------
   Bus stop     |  25, 200
   Engineering Complex |  110, 160
   Dorthy Donahue Building  |  250, 200
   Student Union  |  250, 300
   Walter Stern Library  | 300, 250
   Administration Building | 260  , 50
   
   In addition he must one stop at a  restroom; the available restrooms are at locations (200,160), (340,110), and (280,290)
   
   Find the shortest route freshman Field can take on this visit.  Only 1 restroom stop
   
   
```{r}
x = c(200, 160, 200, 300, 250, 50, 280)
y = c(25, 110, 250, 250, 300, 260, 290)
```

```{r}
tourMAT = ETSP(data.frame(x,y))
tourSolve = solve_TSP(tourMAT)
tour_length(tourSolve)
plot(tourMAT, tourSolve )
```


##   The restroom stop with (280, 290) location gives the shortest route of all - 823.56
